---
title: "Homework 1"
author: "iREM ŞEVVAL POLAT, 19080413"
output: pdf_document
---

```{r global_options, include=FALSE}
# Do not delete or modify this chunk.
# We will cover chunk options later.
# This is required for Question 7
library(knitr)
opts_chunk$set(fig.align="center", fig.height=4, fig.width=5.5)
```

**Question 1** With Markdown write a sentence that has one word in bold.

My favorite teacher is __Emrah Er__.

**Question 2** With Markdown write a sentence that has one word in italic.

My favorite teacher is _Emrah Er_.

**Question 3** With Markdown write a sentence that has one word in italic bold.

My favorite teacher is **_Emrah Er_**

**Question 4** With Markdown write an unordered list with three items.

 * cat
 * coke
 * car

**Question 5** With Markdown write an ordered list with three items.

1. coke
2. cat
3. car

**Question 6** With Markdown give a link to your favorite webpage.

[TikTok](https://www.tiktok.com/tr-TR)

**Question 7** With Markdown add a cat picture.

[cat](https://img-s2.onedio.com/id-62e3ae62752516981dc4f891/rev-0/w-620/f-jpg/s-99fb130edfc0850aac831013236bb232b7d1c173.jpg)



**Question 8** With Rmarkdown insert a code chunk and give an example of a simple mathematical calculation in it.

```{r}
x=5
y=4
x+y
```




**Question 9** With $LaTeX$ write your favorite equation in block form.

$$
\mathbb{E}[X] = \sigma_0 / \sigma_1y
$$



**Question 10** In a code chunk calculate 3 + 4.

```{r}
3+4


```

